Verifying Demonstrations

### 2019-02-14 paper/system-model.tex
Minor edits in system-model

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate of her identity signed by a \ac{CA}.

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital certificate of her 
identity signed by \iac{CA}\footnote{%
  The \ac{CA} must be \emph{logically centralized} to prevent Sybil 
  attacks~\cite{SybilAttack}.
  See \cref{identity-limits} for a discussion on existing identity systems and 
  their limits.
}.
